Dependent Types and Martin-L\"of Type Theory: An Introduction

### 2016-07-25 paper.tex
more
yo

@@

ind𝔹 : (C : 𝔹 → Set) → C True → C False → (x : 𝔹) → C x
ind𝔹 C t f True = t
ind𝔹 C t f False = f
\end{code}
\end{minipage}
\end{center}
%% proof: 1 + 1 = 2

>>>>

We now can write a simple proof that shows the union of \(\top\) and \(\top\)
is equivalent to the Boolean type, that is {\tt ⊤ + ⊤} = {\tt 𝔹}. Alternatively,
since \(\top\) is occasionally written as 1 and {\tt 𝔹} as 2, we name our proof
as follows:
\begin{center}
\begin{minipage}{0.9\textwidth}
\begin{code}
1+1=2 : ⊤ + ⊤ → 𝔹
1+1=2 = ?
\end{code}
\end{minipage}
\end{center}
To do this, we must associate every possible term of type {\tt ⊤ + ⊤} to a
given Boolean (i.e., True or False). This works out quite simply since the
type {\tt ⊤ + ⊤} only has two possible terms, that is {\tt (inl *)} and
{\tt (inr *)}. Thus, we can write the proof as follows:
\begin{center}
\begin{minipage}{0.9\textwidth}
\begin{code}
1+1=2 = rec+ 𝔹 (λ inl* → True) (λ inr* → False)
\end{code}
\end{minipage}
\end{center}
To clarify, this form of equivalence is called ``judmental equality''. We
go over the three different forms of equivalence in the following section.

%% x and Sigma

@@

ind𝔹 : (C : 𝔹 → Set) → C True → C False → (x : 𝔹) → C x
ind𝔹 C t f True = t
ind𝔹 C t f False = f
\end{code}
\end{minipage}
\end{center}
